A biometric analysis of infant mortality and temperature, northern Sweden 1895-1950

### 2022-02-15 paper4.Rmd
add plots of interactions

```{r setformw}
form <- as.formula("oe(event, exposure) ~ extemp + extemp.1 + emeantemp + socst + urban + subreg + sex + parity")
form.sb <-  as.formula("oe(event, exposure) ~ (extemp + extemp.1 + emeantemp) * socst + urban + subreg + sex + parity")
form.sr <- as.formula("oe(event, exposure) ~ (extemp + extemp.1 + emeantemp) * subreg + socst + urban + sex + parity") 
tabpost <- readRDS("data/tabpost.rds")
```

@@

@@

@@

>>>>

```{r setformw}
form <- as.formula("oe(event, exposure) ~ socst + extemp + extemp.1 + emeantemp + urban + subreg + sex + parity")
formex <- as.formula("oe(event, exposure) ~ socst + socst:extemp + extemp.1 + emeantemp + urban + subreg + sex + parity")
formex1 <- as.formula("oe(event, exposure) ~ socst + socst:extemp.1 + extemp + emeantemp + urban + subreg + sex + parity")
formem <- as.formula("oe(event, exposure) ~ socst + socst:I(emeantemp + extemp) + extemp.1 + urban + subreg + sex + parity")
form.sb <-  as.formula("oe(event, exposure) ~ (extemp + extemp.1 + emeantemp) * socst + urban + subreg + sex + parity")
form.sr <- as.formula("oe(event, exposure) ~ (extemp + extemp.1 + emeantemp) * subreg + socst + urban + sex + parity") 
tabpost <- readRDS("data/tabpost.rds")
```

@@

The effects of temperature in different social classes are best shown graphically, see 
Figure \@ref(fig:soc2).

```{r soc1, fig.cap = "Interactions between social status and temperature, winter 1895--1913."}
source("R/socfig.R")
oldpar <- par(mfrow = c(1,3))
tempdat <- tabpost[(!tabpost$summer) & tabpost$period == "(1895,1914]", ]
fit <- tpchreg(formem, data = tempdat, time = age)
fitex <- tpchreg(formex, data = tempdat, time = age)
fitex1 <- tpchreg(formex1, data = tempdat, time = age)
socfig(coef(fit), main = "Weekly mean temp")
socfig(coef(fitex), main = "Excess temp", ran = c(-10, 10))
socfig(coef(fitex1), main = "Lagged excess temp", ran = c(-10, 10))
par(oldpar)
```

@@

The effects of temperature in different social classes are best shown graphically, see 
Figure \@ref(fig:soc2).

```{r soc2, fig.cap = "Interactions between social status and temperature, winter 1914--1934."}
source("R/socfig.R")
oldpar <- par(mfrow = c(1,3))
tempdat <- tabpost[(!tabpost$summer) & tabpost$period == "(1914,1935]", ]
fit <- tpchreg(formem, data = tempdat, time = age)
fitex <- tpchreg(formex, data = tempdat, time = age)
fitex1 <- tpchreg(formex1, data = tempdat, time = age)
socfig(coef(fit), main = "Weekly mean temp")
socfig(coef(fitex), main = "Excess temp", ran = c(-10, 10))
socfig(coef(fitex1), main = "Lagged excess temp", ran = c(-10, 10))
par(oldpar)
```

@@

The effects of temperature in different social classes are best shown graphically, see 
Figure \@ref(fig:soc2).

```{r soc3, fig.cap = "Interactions between social status and temperature, winter 1935--1950."}
source("R/socfig.R")
oldpar <- par(mfrow = c(1,3))
tempdat <- tabpost[(!tabpost$summer) & tabpost$period == "(1935,1951]", ]
fit <- tpchreg(formem, data = tempdat, time = age)
fitex <- tpchreg(formex, data = tempdat, time = age)
fitex1 <- tpchreg(formex1, data = tempdat, time = age)
socfig(coef(fit), main = "Weekly mean temp")
socfig(coef(fitex), main = "Excess temp", ran = c(-10, 10))
socfig(coef(fitex1), main = "Lagged excess temp", ran = c(-10, 10))
par(oldpar)
```
